What's in a name? On the (automated) topic naming of software maintenance activities

### 2010-03-04 icpc/icpc2010.tex
mulan results
Not sure

@@

\subsubsection{Analysing the unsupervised labeling}
Based on the labels, and our manual topic labeling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. Similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes), and the receiver operating characteristic area under curve.

@@

@@

%XXX put mulan stuff here

>>>>

\newcommand{\XXX}[1]{\textcolor{red}{{\it \textbf{[XXX: #1]}}}}

@@

\subsubsection{Analysing the unsupervised labeling}

Based on the labels, and our manual topic labeling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB and MySQL. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. Similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes), and the receiver operating characteristic area under curve.

@@

%XXX Describe learners

@@

\begin{table*}
\begin{tabular}{l|rrrrrrrr}

  & BR & CLR & HOMER & IncludeLabels & LP & MLStacking & MLkNN & RAkEL \\

\hline \\

example-Accuracy & 0.45 & 0.40 & 0.50 & 0.40 & 0.40 & 0.38 & 0.33 & 0.48 \\

example-Fmeasure & 0.56 & 0.48 & 0.59 & 0.47 & 0.49 & 0.46 & 0.40 & 0.55 \\

example-HammingLoss & 0.24 & 0.19 & 0.18 & 0.19 & 0.23 & 0.19 & 0.20 & 0.17 \\

example-Precision & 0.50 & 0.51 & 0.60 & 0.52 & 0.52 & 0.50 & 0.44 & 0.60 \\

example-Recall & 0.65 & 0.46 & 0.58 & 0.44 & 0.47 & 0.43 & 0.37 & 0.52 \\

example-SubsetAccuracy & 0.19 & 0.24 & 0.31 & 0.24 & 0.23 & 0.23 & 0.20 & 0.31 \\

label-macro-AUC & 0.74 & 0.66 & 0.64 & 0.60 & 0.56 & 0.58 & 0.59 & 0.67 \\

label-macro-F1 & 0.46 & 0.30 & 0.43 & 0.28 & 0.32 & 0.27 & 0.22 & 0.39 \\

label-macro-Precision & 0.41 & 0.41 & 0.49 & 0.39 & 0.37 & 0.34 & 0.34 & 0.52 \\

label-macro-Recall & 0.56 & 0.26 & 0.40 & 0.24 & 0.31 & 0.23 & 0.19 & 0.33 \\

label-micro-AUC & 0.81 & 0.81 & 0.77 & 0.77 & 0.66 & 0.80 & 0.80 & 0.79 \\

label-micro-F1 & 0.59 & 0.53 & 0.61 & 0.51 & 0.50 & 0.51 & 0.45 & 0.59 \\

label-micro-Precision & 0.51 & 0.69 & 0.66 & 0.71 & 0.53 & 0.70 & 0.69 & 0.73 \\

label-micro-Recall & 0.68 & 0.43 & 0.56 & 0.41 & 0.48 & 0.41 & 0.34 & 0.49 \\

rank-AvgPrecision & 0.76 & 0.77 & 0.69 & 0.72 & 0.53 & 0.74 & 0.76 & 0.73 \\

rank-Coverage & 1.51 & 1.47 & 1.94 & 1.72 & 2.99 & 1.57 & 1.54 & 2.00 \\

rank-One-error & 0.40 & 0.39 & 0.47 & 0.44 & 0.63 & 0.43 & 0.40 & 0.36 \\

rank-Ranking Loss & 0.19 & 0.18 & 0.27 & 0.22 & 0.52 & 0.20 & 0.19 & 0.28 \\

\end{tabular}
\caption{Mysql Mulan results per Mulan learner}
\end{table*}

\begin{table*}
% Cribbed from:
% src/validate/output/maxdb.mulan.out.tex
\begin{tabular}{l|rrrrrrrr}

  & BR & CLR & HOMER & IncludeLabels & LP & MLStacking & MLkNN & RAkEL \\

\hline \\

example-Accuracy & 0.49 & 0.47 & 0.51 & 0.44 & 0.42 & 0.47 & 0.43 & 0.48 \\

example-Fmeasure & 0.55 & 0.50 & 0.53 & 0.45 & 0.44 & 0.48 & 0.43 & 0.50 \\

example-HammingLoss & 0.19 & 0.14 & 0.14 & 0.14 & 0.17 & 0.13 & 0.13 & 0.13 \\

example-Precision & 0.50 & 0.49 & 0.53 & 0.45 & 0.45 & 0.49 & 0.43 & 0.51 \\

example-Recall & 0.61 & 0.50 & 0.53 & 0.45 & 0.43 & 0.47 & 0.43 & 0.50 \\

example-SubsetAccuracy & 0.40 & 0.43 & 0.45 & 0.43 & 0.38 & 0.43 & 0.43 & 0.43 \\

label-macro-AUC & NaN & NaN & NaN & NaN & NaN & NaN & NaN & NaN \\

label-macro-F1 & 0.32 & 0.19 & 0.23 & 0.11 & 0.19 & 0.12 & 0.00 & 0.26 \\

label-macro-Precision & 0.29 & 0.31 & 0.32 & 0.21 & 0.23 & 0.18 & 0.00 & 0.40 \\

label-macro-Recall & 0.38 & 0.15 & 0.20 & 0.08 & 0.17 & 0.10 & 0.00 & 0.23 \\

label-micro-AUC & 0.76 & 0.66 & 0.62 & 0.55 & 0.62 & 0.68 & 0.65 & 0.68 \\

label-micro-F1 & 0.39 & 0.27 & 0.34 & 0.13 & 0.25 & 0.21 & 0.00 & 0.34 \\

label-micro-Precision & 0.34 & 0.42 & 0.49 & 0.33 & 0.30 & 0.49 & 0.00 & 0.49 \\

label-micro-Recall & 0.47 & 0.21 & 0.26 & 0.09 & 0.22 & 0.14 & 0.00 & 0.27 \\

rank-AvgPrecision & 0.54 & 0.57 & 0.54 & 0.40 & 0.40 & 0.60 & 0.58 & 0.51 \\

rank-Coverage & 1.40 & 1.23 & 1.43 & 1.84 & 1.93 & 1.16 & 1.20 & 1.54 \\

rank-One-error & 0.81 & 0.79 & 0.81 & 0.90 & 0.89 & 0.76 & 0.79 & 0.79 \\

rank-Ranking Loss & 0.41 & 0.35 & 0.41 & 0.58 & 0.60 & 0.32 & 0.33 & 0.46 \\

\end{tabular}

\caption{Maxdb Mulan results per Mulan learner}

\end{table*}
%XXX put mulan stuff here

\subsection{Summary of techniques}

%XXX Compare the results of Exp2 and Exp3 
%    versus the mulan results and weka results
